%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Developer CV
% LaTeX Template
% Version 1.1 (February 24, 2025)
%
% This template originates from:
% https://www.LaTeXTemplates.com
%
% Authors:
% Jan Vorisek (jan@vorisek.me)
% Based on a template by Jan Küster (info@jankuester.com)
% Modified for LaTeX Templates by Vel (vel@LaTeXTemplates.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%  PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[9pt]{config}

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%  TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.45\textwidth}
  \vspace{-\baselineskip}

  \colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Jakub}}}}}
  \colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Sarnowski}}}}}

  \vspace{6pt}

  {\huge Software Engineer}
\end{minipage}
\hfill
\begin{minipage}[t]{0.27\textwidth}
  \vspace{-\baselineskip}

  \icon{MapMarker}{12}{Gniezno, Poland}\\
  \icon{Phone}{12}{+48 785 748 506}\\
  \icon{At}{12}{\href{mailto:hello@jsarnowski.com}{hello@jsarnowski.com}}\\
\end{minipage}
\hfill
\begin{minipage}[t]{0.27\textwidth}
  \vspace{-\baselineskip}

  \icon{Globe}{12}{\href{https://jsarnowski.com}{jsarnowski.com}}\\
  \icon{Github}{12}{\href{https://github.com/jsardev}{github.com/jsardev}}\\
  \icon{Linkedin}{12}{\href{https://www.linkedin.com/in/jsardev}{linkedin.com/in/jsardev}}\\
\end{minipage}

%----------------------------------------------------------------------------------------
%  INTRODUCTION, SKILLS AND TECHNOLOGIES
%----------------------------------------------------------------------------------------

\cvsect{Who Am I?}{}

\begin{minipage}[t]{1\textwidth}
  \vspace{-\baselineskip}

  Passionate about creating software that is visually appealing, intuitive, fast, and enhances user experience. Known for being a great teammate and collaborator, with a commitment to the team and mission. Possess strong technical skills, coupled with a deep understanding of business needs and goals of the products being developed.
\end{minipage}
\hfill

%----------------------------------------------------------------------------------------
%  EXPERIENCE
%----------------------------------------------------------------------------------------

\cvsect{Experience}{(11+ years)}

\begin{entrylist}
\entry
  {07.2025 -- now}
  {Senior Full-stack Developer}
  {\href{https://www.wayfdigital.com/}{WAYF}}
  {
    \listitem{Contributing to development of a large-scale multi-tenant website platform serving 100+ clients.}\\
    \listitem{Maintaining and improving website reliability through comprehensive monitoring systems and protocols.}\\
    \listitem{Developing caching solutions to enhance performance and optimize hosting costs.}\\
  }
  {\texttt{TypeScript}\slashsep\texttt{React}\slashsep\texttt{Next.js}\slashsep\texttt{SCSS}\slashsep\texttt{Contentstack}\slashsep\texttt{Vercel}\slashsep\texttt{GitHub Actions}\slashsep\texttt{Jira}\slashsep\texttt{Confluence}}

  \entry
  {11.2023 -- 05.2025\\\footnotesize 1 year 6 months}
  {Senior Frontend Developer}
  {\href{https://enixware.com}{Enixware}}
  {
    \listitem{Worked on a large-scale web gaming platform serving thousands of concurrent users.}\\
    \listitem{Developed an interactive Web3-based browser game and its accompanying landing page.}\\
    \listitem{Implemented an automated codebase transformation solution, reducing the development time for a large-scale styling migration from 4 weeks to just 1 week.}
  }
  {\texttt{TypeScript}\slashsep\texttt{React}\slashsep\texttt{Astro}\slashsep\texttt{React Router}\slashsep\texttt{React Query}\slashsep\texttt{XState}\slashsep\texttt{Phaser}\slashsep\texttt{Tailwind}\slashsep\texttt{GritQL}\slashsep\texttt{GitHub Actions}\slashsep\texttt{Jira}\slashsep\texttt{Confluence}}

  \entry
  {04.2023 -- 10.2023\\\footnotesize 6 months}
  {Freelancer}
  {\href{https://jsarnowski.com}{Self-employed}}
  {
    \listitem{Worked on a governmental platform for managing citizen-related administrative matters.}\\
    \listitem{Created a comprehensive design system library with reusable components, focusing on high accessibility standards following the WCAG guidelines.}\\
    \listitem{Developed a landing page featuring complex animations and interactions.}
  }
  {\texttt{TypeScript}\slashsep\texttt{React}\slashsep\texttt{GSAP}\slashsep\texttt{React Aria}\slashsep\texttt{Storybook}\slashsep\texttt{Tailwind}\slashsep\texttt{UnoCSS}\slashsep\texttt{GitLab Pipelines}\slashsep\texttt{Jira}\slashsep\texttt{Notion}}

  \entry
  {07.2022 -- 03.2023\\\footnotesize 8 months}
  {Senior Frontend Engineer}
  {\href{https://clickup.com}{ClickUp}}
  {
    \listitem{Worked on a large-scale reactive application, focusing on developing advanced reporting charts and data visualizations.}\\
    \listitem{Led initiative to gather data on performance metrics for data visualizations and general user experience.}
  }
  {\texttt{TypeScript}\slashsep\texttt{Angular}\slashsep\texttt{NgRx}\slashsep\texttt{RxJS}\slashsep\texttt{Nx}\slashsep\texttt{GitHub Actions}\slashsep\texttt{ClickUp}}

  \entry
  {03.2020 -- 06.2022\\\footnotesize 2 years 4 months}
  {Senior Frontend Developer}
  {\href{https://netguru.com}{Netguru}}
  {
    \listitem{Engineered a custom server-side rendering solution for an e-commerce platform, improving the Google Lighthouse performance score by 70 points.}\\
    \listitem{Built the frontend for a home insurance quoting system with complex calculation logic.}\\
    \listitem{Participated in the recruitment process by conducting technical interviews and providing candidates with detailed feedback and growth suggestions.}
  }
  {\texttt{TypeScript}\slashsep\texttt{Node.js}\slashsep\texttt{React}\slashsep\texttt{Next.js}\slashsep\texttt{Razzle}\slashsep\texttt{Redux}\slashsep\texttt{MobX}\slashsep\texttt{Storyblok}\slashsep\texttt{Google Cloud}\slashsep\texttt{Jira}\slashsep\texttt{Confluence}}

  \entry
  {07.2019 -- 02.2020\\\footnotesize 8 months}
  {React Developer}
  {ST-YL}
  {
    \listitem{Worked on an e-commerce web application in the clothing industry.}\\
    \listitem{Enhanced performance by identifying and resolving loading issues, resulting in a 50\% improvement in LCP.}\\
    \listitem{Implemented search and filtering capabilities, along with advanced analytics.}\\
    \listitem{Customized a CMS for the marketing team to easily launch campaigns, integrating it with the storefront for dynamic content.}
  }
  {\texttt{TypeScript}\slashsep\texttt{React}\slashsep\texttt{Next.js}\slashsep\texttt{Redux}\slashsep\texttt{Redux Form}\slashsep\texttt{Reselect}\slashsep\texttt{Strapi}\slashsep\texttt{GitHub Actions}\slashsep\texttt{Jira}\slashsep\texttt{Confluence}}

  \entry
  {01.2018 -- 06.2019\\\footnotesize 1 year 6 months}
  {Freelancer}
  {\href{https://jsarnowski.com}{Self-employed}}
  {
    \listitem{Developed brand identity and software solutions for a personal trainer, managing the full technology stack and deployment infrastructure.}\\
    \listitem{Collaborated closely with the client to ensure software capabilities aligned with the brand's vision.}\\
    \listitem{Implemented secure payment processing and a subscription management system.}\\
    \listitem{Improved the client's conversion rate by 20\% through a custom-coded landing page.}
  }
  {\texttt{JavaScript}\slashsep\texttt{Next.js}\slashsep\texttt{React}\slashsep\texttt{Fastify}\slashsep\texttt{Ramda}\slashsep\texttt{Stripe}\slashsep\texttt{GitHub Actions}\slashsep\texttt{Trello}}

  \entry
  {05.2017 -- 12.2017\\\footnotesize 8 months}
  {Software Engineer}
  {\href{https://allegro.pl}{Allegro}}
  {
    \listitem{Built large-scale applications and microservices in a distributed infrastructure, handling orchestration and DevOps aspects.}\\
    \listitem{Engaged in product design and planning, including discussing requirements and creating roadmaps.}\\
    \listitem{Collaborated effectively within the team following SCRUM methodology and provided mentorship to junior developers.}\\
    \listitem{Maintained and improved outdated systems, optimizing resource usage.}
  }
  {\texttt{JavaScript}\slashsep\texttt{React}\slashsep\texttt{Redux}\slashsep\texttt{Node.js}\slashsep\texttt{Koa}\slashsep\texttt{Express}\slashsep\texttt{Java}\slashsep\texttt{Kotlin}\slashsep\texttt{Spring}\slashsep\texttt{PHP}\slashsep\texttt{Symfony}\slashsep\texttt{Kafka}\slashsep\texttt{Hermes}\slashsep\texttt{Consul}\slashsep\texttt{Mesos}\slashsep\texttt{Marathon}\slashsep\texttt{Bamboo}\slashsep\texttt{Jira}\slashsep\texttt{Confluence}}

  \entry
  {01.2016 -- 04.2017\\\footnotesize 1 year 4 months}
  {Junior Software Engineer}
  {\href{https://allegro.pl}{Allegro}}
  {
    \listitem{Independently worked on a complex application, actively solving problems and engaging in code reviews to enhance learning and independence.}\\
    \listitem{Shared knowledge with team members by teaching aspiring Software Engineers and offering test engineering insights.}
  }
  {\texttt{JavaScript}\slashsep\texttt{React}\slashsep\texttt{Redux}\slashsep\texttt{Java}\slashsep\texttt{Spring}\slashsep\texttt{Bamboo}\slashsep\texttt{Jira}\slashsep\texttt{Confluence}}

  \entry
  {01.2015 -- 12.2015\\\footnotesize 1 year}
  {Junior Software Tester}
  {\href{https://allegro.pl}{Allegro}}
  {
    \listitem{Created automated tests for a microservices-based infrastructure, including multi-browser tests and scheduled jobs for continuous integration.}\\
    \listitem{Proposed new technologies to enhance developer experience and worked to improve the company's focus on product quality.}\\
    \listitem{Developed clear and replicable bug reports with detailed reproduction steps and prepared test environments.}
  }
  {\texttt{JavaScript}\slashsep\texttt{Java}\slashsep\texttt{Selenium}\slashsep\texttt{Selenium Grid}\slashsep\texttt{JMeter}\slashsep\texttt{Bamboo}\slashsep\texttt{Jira}\slashsep\texttt{Confluence}}

  \entry
  {01.2015 -- 02.2016\\\footnotesize 1 year 2 months\\}
  {Junior .NET Developer}
  {\href{https://mtab.com}{mTab}}
  {}
  {}

  \entry
  {10.2013 -- 12.2014\\\footnotesize 1 year 3 months\\}
  {Software Tester}
  {\href{https://mtab.com}{mTab}}
  {}
  {}
\end{entrylist}

%----------------------------------------------------------------------------------------
%  EDUCATION
%----------------------------------------------------------------------------------------

\cvsect{Education}{}

\begin{entrylist}
  \entry
  {2013 -- 2014}
  {Bachelor of Software Engineering}
  {Wyższa Szkoła Bankowa}
  {Pursued comprehensive software engineering studies, focusing on
    the principles of designing, developing, and maintaining efficient
    software systems. Left the program after one year to gain more
  practical, hands-on experience by working at a software company.}
  {}
\end{entrylist}

%----------------------------------------------------------------------------------------
%  ADDITIONAL INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.3\textwidth}
  \vspace{-\baselineskip}

  \cvsect{Languages}{}

  \textbf{Polish} - native\\
  \textbf{English} - advanced\\
  \textbf{German} - basic\\
\end{minipage}
\hfill
\begin{minipage}[t]{0.3\textwidth}
  \vspace{-\baselineskip}

  \cvsect{Hobbies}{}

  Passionate about music and game development.
\end{minipage}
\hfill
\begin{minipage}[t]{0.3\textwidth}
  \vspace{-\baselineskip}

  \cvsect{Non profit}{}

  Volunteered at a nonprofit to teach children programming concepts
  using Scratch, creating an engaging and supportive environment.
\end{minipage}

%----------------------------------------------------------------------------------------

\end{document}
